Bayes Exploration with Brms

### 2023-08-14 Misc/Distributional_Explore.qmd
reorganize

---
title: "Distributional_Explorations"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
---

>>>>

---
title: "Distributional_Explorations"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
execute: 
  warning: false
  eval: false
---

### 2023-08-14 Misc/e1_brms_test.qmd
reorganize

---
title: "E1 Testing - Bayesian Mixed Models"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
---

>>>>

---
title: "E1 Testing - Bayesian Mixed Models"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
execute: 
  warning: false
  eval: false
---

### 2023-08-14 Misc/scratch/bayes_explore.qmd
Indv tables function, and some reorganization
reorganize

---
title: "Bayes Exploration with Brms"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
---

@@

>>>>

---
title: "Bayes Exploration with Brms"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
execute: 
  warning: false
  eval: false
---

@@

parameters::model_parameters(fit_int_norm)
